The connection between star formation rate and dark matter halo mass in the epoch of reionization

### 2015-04-23 paper/ms.tex
figures updated. fontsize corrected.

\shortauthors{Gomez, Forero-Romero}

\author{Felipe Gomez, Jaime E. Forero-Romero}  
\affil{Departamento de F\'{i}sica, Universidad de los Andes, Cra. 1
No. 18A-10, Edificio Ip, Bogot\'a, Colombia}
\email{fl.gomez10@uniandes.edu.co}
\email{je.forero@uniandes.edu.co}

@@

First of all, one of the four observational data sets (Bouwens, Finkelstein, Willow and McLure) 
is selected to be the model to fit.
From the whole simulated halo catalog, a subsample with cubic box shape of 
 $250\textrm{Mpc h}^{-1}$ length is selected.

@@

\begin{figure}
\epsscale{1.00}
\plotone{fig/OD3_w_15.pdf}
\caption{Parameter dispersion: The 10.000 MCMC step parameters histogram for OD3 over the small boxe 15
with dust attenuation.}
\label{fig:ParamDispWithDust}
\end{figure}

\begin{figure}
\epsscale{1.00}
\plotone{fig/OD3_wo_15.pdf}
\caption{Parameter dispersion: The 10.000 MCMC step parameters histogram for OD3 over the small boxe 15
with dust attenuation.}
\label{fig:ParamDispWithoutDust}
\end{figure}

$\gamma$ always has the best coincidence for the minimum at the 10\%.

\begin{figure}
\epsscale{1.00}
\plotone{fig/bestpar_disp_w_OD3.pdf}
\caption{Cosmic Variance: The best fit parameters histogram for OD3 over the 64 small boxes 
with dust attenuation.}
\label{fig:ParamScatteringWithDust}
\end{figure}

\begin{figure}
\epsscale{1.00}
\plotone{fig/bestpar_disp_w_OD3.pdf}
\caption{Cosmic Variance: The best fit parameters histogram for OD3 over the 64 small boxes 
without dust attenuation.}
\label{fig:ParamScatteringWithoutDust}
\end{figure}

\begin{figure}
\epsscale{1.00}
\plotone{fig/scattering_plots.png}
\caption{Covariance of parameters for one small box}
\label{graph_scattering_plots}
\end{figure}

>>>>

\shortauthors{Gomez-Cortes, Forero-Romero}

\author{Felipe L. Gomez-Cortes, Jaime E. Forero-Romero}  
\affil{Departamento de F\'{i}sica, Universidad de los Andes, Cra. 1
No. 18A-10, Edificio Ip, Bogot\'a, Colombia}
\email{fl.gomez10@uniandes.edu.co}
\email{je.forero@uniandes.edu.co}

@@

First of all, one of the four observational data sets (Bouwens, Finkelstein, Willott and McLure) 
is selected to be the model to fit.
From the whole simulated halo catalog, a subsample with cubic box shape of 
 $250\textrm{Mpc h}^{-1}$ length is selected.

@@

Best fit parameters:

Cosmic Variance Dust Attenuation model:

$\log_{10}(L_0)$, mean value = 18.0668181805, 
cosmic std dev=0.0288558407431, 
mean sigma per box =0.115498563539

$\log_{10}(M_0)$, mean value = 11.1894829902, 
cosmic std dev=0.0718242117247, mean 
sigma per box =0.72909362196

$\beta$, mean value = 1.48014744519, 
cosmic std dev=0.175026973523, 
mean sigma per box =1.2988714515

$\gamma$, mean value = 0.402845130968, 
cosmic std dev=0.0575764062455, 
mean sigma per box =0.314709555486

\medskip

Cosmic Variance No-Dust Attenuation model:

$\log_{10}(L_0)$, mean value = 17.8076246968, 
cosmic std dev=0.0198125186745, 
mean sigma per box =0.150082796188

$\log_{10}(M_0)$, mean value = 11.119460579, 
smic std dev=0.0601358065131, 
mean sigma per box =0.642532804052

$\beta$, mean value = 1.43705896343, 
cosmic std dev=0.178253100134, 
mean sigma per box =1.37416358513

$\gamma$, mean value = 0.518242492031, 
cosmic std dev=0.0461244563387, 
mean sigma per box =0.245817572122

\begin{figure}
\epsscale{1.00}
\plotone{fig/OD1_chi2_comparison.pdf}
\caption{Best fit to Willott comparison between the two models. Each point represent $\chi^2$ 
calculated over each small-box. The solid line represents the ratio 1:1 }
\label{fig:OD1_chi2_comparison}
\end{figure}

\begin{figure*}
\epsscale{1.00}
\plotone{fig/OD1_w_dust_box_0.png} % pdf available
\caption{Parameter dispersion fitting the Willott with the Dust Attenuation model. 
$1\sigma$ is defined by the likelihood ratio between 0.0 (red) and 0.5 (green)}
\label{}
\end{figure*}

\begin{figure*}
\epsscale{1.00}
\plotone{fig/OD1_wo_dust_box_0.png} % pdf available
\caption{Parameter dispersion fitting the Willott with the No-Dust Attenuation model. 
$1\sigma$ is defined by the likelihood ratio between 0.0 (red) and 0.5 (green)}
\label{}
\end{figure*}

\begin{figure}
\epsscale{1.00}
\plotone{fig/OD1_CosmicVar1_w_dust.pdf}
\caption{Individual small-box parameter estimation with dust attenuation: Best fit values 
to the Willott data set
(solid line) and $1\sigma$ confidence interval using likelihood ratio $\mathcal{LR}= 0.5$. 
The $x$ axis corresponds to the box number.}
\label{}
\end{figure}

\begin{figure}
\epsscale{1.00}
\plotone{fig/OD1_CosmicVar1_wo_dust.pdf}
\caption{Individual small-box parameter estimation with no-dust attenuation: Best fit values 
to the Willott data set
(solid line) and $1\sigma$ confidence interval using likelihood ratio $\mathcal{LR}= 0.5$. 
The $x$ axis corresponds to the box number.}
\label{}
\end{figure}

\begin{figure}
\epsscale{1.00}
\plotone{fig/OD1_CosmicVar2_w_dust.pdf}
\caption{Best fit parameter distribution due cosmic variance with Willott data in the dust
 attenuation model.}
\label{}
\end{figure}

\begin{figure}
\epsscale{1.00}
\plotone{fig/OD1_CosmicVar2_wo_dust.pdf}
\caption{Best fit parameter distribution due cosmic variance with Willott data in the no-dust
 attenuation model.}
\label{}
\end{figure}
